### 2018-07-06 paper/5-implementations.tex
S5 update suspending to use liftRun and be actually recursive

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system; stores verifying traces
shake :: (Ord k, Hashable v) => Build Monad (VT k v) k v
shake = suspending vtRebuilder
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A task rebuilder based on verifying traces
vtRebuilder :: (Eq k, Hashable v) => Rebuilder Monad (VT k v) k v
vtRebuilder key value task = Task $ \fetch -> do
    upToDate <- verifyVT key (hash value) (fmap hash . fetch) =<< get
    if upToDate then return value else do
        (newValue, deps) <- track task fetch
        modify $ recordVT key (hash newValue) [ (k, hash v) | (k, v) <- deps ]
        return newValue
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A suspending task scheduler
suspending :: Ord k => Scheduler Monad i i k v
suspending rebuilder tasks target store = fst $ execState (build target) (store, Set.empty)
  where
    build :: k -> State (Store i k v, Set k) (@@)
    build key = case tasks key of
        Nothing -> return (@@)
        Just task -> do
            done <- gets snd
            when (key `Set.notMember` done) $ do
                value <- gets (getValue key . fst)
                let newTask :: Task (MonadState i) k v
                    newTask = rebuilder key value task
                    fetch :: k -> StateT i (State (Store i k v, Set k)) v
                    fetch k = do lift (build k)                      -- build the key
                                 lift (gets (getInfo . fst)) >>= put -- save new traces
                                 lift (gets (getValue k . fst))      -- fetch the value
                newValue <- flattenInfo (run newTask fetch)
                modify $ \(s, d) -> (putValue key newValue s, Set.insert key d)
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Collapse two layers of stateful computations into one (implementation omitted)
flattenInfo :: StateT i (State (Store i k v, Set k)) a -> State (Store i k v, Set k) a
\end{minted}
\vspace{-3mm}
\caption{An implementation of \Shake using our framework.}\label{fig-shake-implementation}
\vspace{-6mm}
\end{figure}

@@

These steps are run in the
\hs{StateT}~\hs{i}~\hs{(@@State}~\hs{(@@Store}~\hs{i}~\hs{k}~\hs{v,}~\hs{Set}~\hs{k))}
monad, because the \hs{newTask} has access only to the~\hs{i} part of the state;
we therefore need to use \hs{lift} when executing commands in the inner
\hs{State}~\hs{(@@Store}~\hs{i}~\hs{k}~\hs{v,}~\hs{Set}~\hs{k)} monad.
We use the helper function \hs{flattenInfo} to collapse two layers of stateful
computations into one. The \hs{newValue} obtained by running the \hs{newTask} is
stored, and the \hs{key} is added to the set \hs{done}.

>>>>

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system; stores verifying traces
shake :: (Ord k, Hashable v) => Build Monad (VT k v) k v
shake = suspending vtRebuilder
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A task rebuilder based on verifying traces
vtRebuilder :: (Eq k, Hashable v) => Rebuilder Monad (VT k v) k v
vtRebuilder key value task = Task $ \fetch -> do
    upToDate <- verifyVT key (hash value) (fmap hash . fetch) =<< get
    if upToDate then return value else do
        (newValue, deps) <- track task fetch
        modify $ recordVT key (hash newValue) [ (k, hash v) | (k, v) <- deps ]
        return newValue
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A suspending task scheduler
suspending :: Ord k => Scheduler Monad i i k v
suspending rebuilder tasks target store = fst $ execState (build target) (store, Set.empty)
  where
    build :: k -> State (Store i k v, Set k) v
    build key = do
        done <- gets snd
        case tasks key of
            Just task | key `Set.notMember` done -> do
                value <- gets (getValue key . fst)
                let newTask :: Task (MonadState i) k v
                    newTask = rebuilder key value task
                newValue <- liftRun newTask build
                modify $ \(s, d) -> (updateValue key value newValue s, Set.insert key d)
                return newValue
            _ -> gets (getValue key . fst) -- fetch the existing value
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Run a Task using Store to obtain the i
liftRun :: Task (MonadState i) k v
        -> (k -> State (Store i k v, Set k) v) -> State (Store i k v, Set k) v
\end{minted}
\vspace{-3mm}
\caption{An implementation of \Shake using our framework.}\label{fig-shake-implementation}
\vspace{-6mm}
\end{figure}

@@

These steps are run in the
\hs{State}~\hs{(@@Store}~\hs{i}~\hs{k}~\hs{v,}~\hs{Set}~\hs{k)}
monad. To make \hs{MonadState}~\hs{i} access the \hs{i} inside the \hs{Store}
we use the helper function \hs{liftRun} (which uses a \hs{newtype} to provide a \hs{MonadState}
instance that sees through into the \hs{Store}).
The \hs{newValue} obtained by running the \hs{newTask} is
stored, and the \hs{key} is added to the set \hs{done}.
